Outflows and rotation in Lyman alpha emitting galaxies

### 2017-04-06 paper/paper.tex
list of models

For each model setup we follow $10^4$ individual photons generated at
the center of the sphere at the \lya\ line's center as they propagate
through the spere and finally scape.
We store the final frequency and propagation direction for each photon
at its last scattering.

@@

\cite{Garavito14} presented in the Appendix an analytical model that
accounts for these two features.
The basic assumption of the analytical model is that each
differential surface element on the sphere Doppler shifts the photons
that it emmits.

@@

\begin{table}[htbp]
	\centering
	\begin{tabular}{|c|c|c|}
		\hline
		$\tau_{\mathrm{H}}$ & $v_{rot}$ (\kms) & $v_{out}$ (\kms) \\
		\hline
		$10^5$, $10^6$, $10^7$ & 50, 100 & 5, 10, 15, 20, 25, 50, 75 \\
		\hline
	\end{tabular}
	\caption{\textbf{Parameters' Values:} All consistent with a LAE's typical properties}
	\label{tab:values}
\end{table}

>>>>

For each model setup we follow $10^5$ individual photons generated at
the center of the sphere at the \lya\ line's center as they propagate
through the spere and finally scape.
We store the final frequency and propagation direction for each photon
at its last scattering.

In Table \ref{tab:values} we list the combination of $\tau_{\rm{H}}$,
$v_{rot}$ and $v_{out}$ values used in this paper.
The range of values have some overlap with the expectations from a dwarf
galaxy with a total neutral hydrogen mass of $10^8$-$10^9$ $M_{\odot}$.
We run a total of $21$ different models.

\begin{table}[htbp]
  \begin{center}
    \begin{tabular}{|c|c|c|}
      \hline
      $\tau_{\mathrm{H}}$ & $v_{rot}$ (\kms) & $v_{out}$ (\kms) \\
      \hline
      $10^5$  & \{0, 50, 100\} & \{25, 50\} \\
      $10^6$ & \{0, 50, 100\} & \{25, 50\}\\
      $10^7$ & \{0, 50\} & \{25, 50\}\\
      $10^7$ & \{0, 100\} & \{50, 100, 200\}\\
      \hline    
    \end{tabular}
  \end{center}
  \caption{\textbf{Parameters' Values.} List of values that were used
    to construct the radiative transfer models. Values in braces
    for a row indicate that all possible combinations in of
    $\tau_{\rm{H}}$,
    $v_{rot}$ and $v_{out}$ are used.}
  \label{tab:values}
\end{table}

@@

\cite{Garavito14} presented in the Appendix an analytical model that
accounts for these two features.
The basic assumption of the analytical model is that each
differential surface element on the sphere Doppler shifts the photons
that it emmits.
In this paper we introduce this ansatz by postprocessing the results
of the outflow simulations without rotation.
This allows us to produce new \lya spectra and compare them with the
full radiative transfer solution including both outflows and
rotation.

@@
